Abstractions for Multi-Sorted Substitutions

### 2024-03-14 paper/paper.tex
Update.

  \subsection{Fibrational}
  \cite{DBLP:conf/rta/LicataSR17}

  \subsection{Pure Type Systems}
  \cite{DBLP:conf/esop/BarendregtH90, berarditowards, terlouw1989een}

>>>>

  % \subsection{Fibrational}
  % \cite{DBLP:conf/rta/LicataSR17}

  \subsection{Pure Type Systems}
  Pure Type Systems\cite{DBLP:conf/esop/BarendregtH90, berarditowards, terlouw1989een}
  describe a class of typed lambda calculi parameterized over a set of
  sorts, dependencies between sorts, and rules for quantification.

  While pure type systems may seem very similar to multi-sorted
  syntax, they are actually quite different:
  \begin{itemize}
  \item 
    In multi-sorted syntax, sorts describe syntactic categories of terms. Terms
    of different sorts are kept syntactically different, e.g. the set of expressions
    \ACode{S ⊢ 𝕖} and types \ACode{S ⊢ 𝕥} in our System F example.
  \item 
    In pure type systems, sorts are universes, e.g. as
    in Agda a type has itself type \ACode{Set} or a kind has type \ACode{Set₁}.
    Terms which have different sorts as types, do still belong to the
    same syntactic category.
  \end{itemize}

  We can use our framework to model pure type systems, but the sorts of pure type systems
  do not correspond to the sorts of the multi-sorted syntax. The multi-sorted syntax
  has just a single sort that describes all terms, as it is common for
  dependently typed languages.
